\section{Acknowledgements}

We are indebted to the Livermore Computing Center for access to Sierra and help getting set up there.
In particular, our contacts John Gyllenhal and Adam Bertsch were very helpful and responsive, and other early users were very cooperative and collaborative, keeping us appraised of the state of the machine, difficulties they encountered, and workarounds.  In particular, Jim Glosli, Tomas Oppelstrup, and especially Tom Scogland were very generous with their time and concern.  At the Oak Ridge Leadership Computing Facility, Jack Wells provided excellent help, advice, and encouragement.

An award of computer time was provided by the Innovative and Novel Computational Impact on Theory and Experiment (INCITE) program to CalLat (2016) as well as the Lawrence Livermore National Laboratory (LLNL) Multiprogrammatic and Institutional Computing program through a Tier 1 Grand Challenge award. This research used the NVIDIA GPU-accelerated Titan and Summit supercomputers at the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC05-00OR22725, and the NVIDIA GPU-accelerated Surface, Ray, and Sierra supercomputers LLNL.  This work was performed under the auspices of the U.S. Department of Energy by LLNL under Contract No. DE-AC52-07NA27344 and under contract DE-AC02-05CH11231, which the Regents of the University of California manage and operate Lawrence Berkeley National Laboratory and the National Energy Research Scientific Computing Center.
